Title

### 2013-02-23 inc/model_results/lens_charge/lens_charge.tex
improve plots for lens_charge

The single-electron ($ N = 1 $) focal spot sizes of $\sim$150 microns for the $ f = 60 \text{mm} $ lens and $\sim$15 microns for the shorter $ f = 6.0 \text{mm} $ lens show marked increase starting around $ N \approx 10^{ 5 } $ and $ N \approx 10^{ 6 }$, respectively, and worsening dramatically above these thresholds.
This order of magnitude difference is fundamentally related to the greater time of flight before the focus of the $ f = 60\text{mm} $ lens; it increases the impulse that the internal Coulomb force can exert on the pulse as its charge density is increased under focusing.
A consequent further effect is a shift in the focal position to $ z > f $.
%A more subtle effect is that disk-like pulses are more readily focused than cigar-like pulses --- the rate of transverse pulse broadening due to space-charge effects already being intrinsically greater in the latter (\Fig \ref{fig:compare}). Thus, the electron pulse propagation model predicts that higher fidelity focusing will be achieved with shorter focal length magnetic lenses, higher acceleration energy electrons (time of flight reduction), and pulses with $ \sigma_{ \smallT } \gg \sigma_{ z } $ at the entrance aperture of the lens.

>>>>

The single-electron ($ N = 1 $) focal spot sizes of $\sim$150 microns for the $ f = 60 \text{mm} $ lens and $\sim$15 microns for the shorter $ f = 6.0 \text{mm} $ lens show marked increase starting around $ N \approx 10^{ 5 } $ and $ N \approx 10^{ 6 }$, respectively, and worsening dramatically above these thresholds.
This order of magnitude difference is fundamentally related to the greater time of flight before the focus of the $ f = 60\text{mm} $ lens; it increases the impulse that the internal Coulomb force can exert on the pulse as its charge density is increased under focusing.
A consequent further effect is a shift in the focal position to $ z > f $.
%A more subtle effect is that disk-like pulses are more readily focused than cigar-like pulses --- the rate of transverse pulse broadening due to space-charge effects already being intrinsically greater in the latter (\Fig \ref{fig:compare}).

%TODO? include simulations for different voltages to establish TOF argument?

Thus, the extended AG electron pulse propagation model predicts that higher fidelity focusing will be achieved with shorter focal length magnetic lenses, higher acceleration energy electrons (time of flight reduction), and pulses with $ \sigma_{ \smallT } \gg \sigma_{ z } $ at the entrance aperture of the lens.
